---
title: "BSMM-lab-4"
subtitle: "BSMM 8740 Fall 2023"
author: "Add your name here"
date: "Add the date here"
format: html
editor: visual
self-contained: true
---

::: callout-note
## REMINDER:

Be sure to edit this document (see above) to include your name (and the date)
:::

## Setup

Load packages and data:

```{r load-pkg-data}
#| message: false
boston <- ISLR2::Boston
```

## Exercises

### Exercise 1

The intercept and the coefficient of `lstat` in this model are: intercept = \_\_; coefficient = \_\_

### Exercise 2

Are there any overly influential observations in this dataset?

### Exercise 3

Which predictors in this dataset might be redundant for predicting `medv`?

### Exercise 4

Which model returns the (approximately) correct dependence of demand on price, as given in the data generation process?

lm(demand0 \~ price0) or lm(demand1 \~ price1) ?

### Exercise 5

After controling for the unobservable covariates, hich model now returns the (approximately) correct dependence of demand on price, as given in the data generation process?

lm(demand0 \~ price0 + unobserved0) or lm(demand1 \~ price1 + unobserved1) ?

What can you conclude from these exercises 4 and 5?

### Exercise 6

```{r}
#| echo: true
#| eval: false
dat <- 
  readxl::read_xlsx("data/2023 FE Guide for DOE-release dates before 7-28-2023.xlsx")
```

How many predictor variables are there in `cars_23` ?

### Exercise 7

After these two steps how many columns are in the data? Why does this differ from the last step?

### Exercise 8

The RMSE for the un-tuned model is \_\_.

### Exercise 9

Is the tuned model better than the un-tuned model? If better, how much has the RMSE improved (in %).

### Exercise 10

Per this model, what is the most important feature for predicting fuel efficiency?
